---
title: "What the Subscribers Read"
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Data prep
# ---------------------------------------------
library(tidyverse)
library(readxl)

# Topics
topic_1840s <- read_xlsx("../data-raw/Topics - 1840s.xlsx")
topic_1850s <- read_xlsx("../data-raw/Topics - 1850s.xlsx")
topic_1860s <- read_xlsx("../data-raw/Topics - 1860s.xlsx")
topic_1870s <- read_xlsx("../data-raw/Topics - 1870s.xlsx")
topic_1880s <- read_xlsx("../data-raw/Topics - 1880s.xlsx")
topic_1890s <- read_xlsx("../data-raw/Topics - 1890s.xlsx")

topic_1840s$decade <- paste0("1840")
topic_1850s$decade <- paste0("1850")
topic_1860s$decade <- paste0("1860")
topic_1870s$decade <- paste0("1870")
topic_1880s$decade <- paste0("1880")
topic_1890s$decade <- paste0("1890")

topics <- rbind(topic_1840s, topic_1850s, topic_1860s, topic_1870s, topic_1880s, topic_1890s)
names(topics) <- tolower(names(topics))
```

Topics in the newspapers hosted in this project show various aspects of early Black communities in Ohio. First, we can see what contemporary readers looked for in the newspaper. Their interests reveal the relationship that individual readers had with their community at familial, local, national, and even international levels. Second, newspaper topics tell what editors and publishers aimed at through its publication. Like most Black periodicals in the 19th century, publishing newspapers in Ohio was an unprofitable business, for which editors and publishers often had to maintain jobs other than working for the paper until Harry Smith as a full-time newspaperman started the Cleveland Gazette in 1883. Their occupations included barbers, preachers, educators, civil servants, librarians, business owners, but, of course, not limited to these. The diversity of the editors also implies that they helped the newspaper address manifold interests of various groups within the Black community. Third, topics in the newspaper lead us to hidden and anonymous contributors, most of whom were women and children, because their presence in public, even with only names in print, was considered inappropriate in the contemporaneous culture of the cult of womanhood. At last, the topic data reflects how Black Ohioans responded to historical moments in the 19th-century U.S. in order to achieve civil rights and demonstrate their civic qualification as model citizens. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(plotly)
library(ggthemes)

# Chronological change of topics

# Small multiples
top <- ggplot(topics, aes(x = decade, y = frequency)) +
  geom_bar(stat="identity") +
  facet_wrap(~topic, ncol = 2) +
  theme_minimal() +
  theme(legend.position="none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
#top

top_plotly <- ggplotly(top, width = 800, height = 800)
top_plotly
```

While politics steadily remained to be a priority, new topics such as morality and house management emerged significantly, as newspapers aimed at more diversifying readership in the later nineteenth-century. This change also implies that Black residents in Ohio at the end of the century had a political influence, bolstered by the growth of their economic and cultural power, more than the earlier generations. 

Data of the newspaper topics were collected from the sixteen available newspapers. The categories for the data include literature (short stories, poetry, and drama), morality, Christianity (sermon and church activities), education, politics (elections, colonialism, civil rights movement, and abolitionism), international affairs, humor, crime and justice, community event (conventions of Black citizens), business and economy, and home management. The data measures both frequency and length of a topic because they are not necessarily congruent with each other. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Stacked
top_stacked <- ggplot(topics, aes(x = decade, y = frequency, fill = topic)) +
  geom_bar(stat="identity", color="black") +
  scale_fill_brewer(type = "qual", palette = "Set3") +
  theme(legend.position="none")
#top_stacked

stacked_plotly <- ggplotly(top_stacked, width = 800, height = 800)
stacked_plotly
```
